The CrypTool Script: \\ Cryptography, Mathematics and More \\ \vspace{30pt} {\large Background reading\\%*[-8pt] for the free e-learning program CrypTool\\ (10th edition -- distributed with CrypTool version 1.4.30)} \vspace{60pt}

### 2012-10-11 script/en/chapters/movies.tex
Small corrections and enhancements in the CT Script

\item[\textrm{[Suarez2010]}] \index{Suarez 2010}
    Daniel Suarez, \\
    {\em Freedom (TM)}, Penguin Books, 2010, 486 pages. \\
    ``The propulsive, shockingly plausible sequel to the bestseller Daemon'' (see above).
    Freedom (TM) (Daemon \#2) patches a number of holes the writer left in the first book.
    The prose is tighter, the descriptions more direct, the characters are fleshed out.
    Having laid all the groundwork in ``Daemon'', Suarez uses most of this book to use this
    foundation in order to explore a new concept of social organization based on empowering
    information technology and the reasoning why and how the battle runs between the old
    potentates and the Daemon society, which also evolves further during the story.
    Cryptography is a natural part of modern technology and modern warfare as described
    in this book.
    The new society emerging in "Freedom (TM)" is based on the darknet, an alternative to
    the internet using fast wireless meshes in order to increase the durability and
    availability of the network. Its not far away from the parallel usage of modern
    technology integrated into our modern lives as a virtual world overlaying our real
    world.\\

@@

>>>>

\item[\textrm{[Suarez2010]}] \index{Suarez 2010}
    Daniel Suarez, \\
    {\em Freedom (TM)}, Penguin Books, 2010, 486 pages. \\
    ``The propulsive, shockingly plausible sequel to the bestseller Daemon'' (see above).
    Freedom (TM) (Daemon \#2) patches a number of holes the writer left in the first book.
    The prose is tighter, the descriptions more direct, the characters are fleshed out,
    especially Loki.
    Having laid the groundwork in ``Daemon'', Suarez uses this
    foundation in order to explore a new concept of social organization based on empowering
    information technology and the reasoning why and how the battle runs between the old
    potentates and the Daemon society, which also evolves further already during the story.
    Cryptography is a natural part of modern technology and modern warfare as described
    in this book.
    The new society emerging in "Freedom (TM)" is based on the darknet, an alternative to
    the internet using fast wireless meshes in order to increase the durability and
    availability of the network. Despite the story is shocking in some parts, it appears to
    be realistic and not far away from the parallel usage of modern technology integrated
    into our modern lives as a virtual world overlaying our real world.\\

@@

\item[\textrm{[Elsberg2012]}] \index{Elsberg 2012}
    Marc Elsberg, \\
    {\em Blackout -- Tomorrow its too late (original title: Blackout -- Morgen ist
    es zu sp\"at)},\\ Blanvalet, 2012, 800 pages. \\
    At a could day in winter all power supply networks in Europe break down.
    Agencies, energy suppliers and security companies are in the dark and unable to solve
    the problem.
    The Italian computer scientist Piero Manzano believes that this caused by terrorists
    using hackers: All customers use since some years smart meters, electricity meters
    controlled by software which was manipulated. Despite the integrated security and encryption
    components they have been hacked, and are out of order by wrong control sequences.
    The terrifying consequences at various locations are described realistically and excitingly.
    And in the same way the reactions of the human beings ...\\
